Detect Pharmaceutical Quality Deviations with MS, Raman and Statistics

### 2024-12-10 dev/demo_paracetamol_fusion.Rmd
3d plot raman spectra

main_dir <- "C:/Users/apoli/Documents/example_files/isoft/Paracetamol_subset" # Ricardo laptop
ms_dir <- paste0(main_dir, "/ms")
ms_files <- list.files(ms_dir, pattern = ".mzML$", full.names = TRUE)
raman_dir <- paste0(main_dir, "/raman")
raman_files <- list.files(raman_dir, pattern = ".asc$", full.names = TRUE)
```

@@

```{r sets-show}
main_set_idx <- c(1:10)

@@

```{r sets-show-knn}
train_idx <- grep("_1|_2|_01|_04|_06|_10", rownames(fused_mat))

@@

```{r sets-show}
main_set_idx <- c(1:10)
ms_main_set <- ms_spec_mat[main_set_idx, ]
rownames(ms_main_set)
ms_test_set <- ms_spec_mat[-main_set_idx, ]
rownames(ms_test_set)
```

@@

```{r sets-show-knn}
train_idx <- grep("_1|_2|_01|_04|_06|_10", rownames(ms_spec_mat))

@@

```{r sets-show}
main_set_idx <- c(1:10)
raman_main_set <- raman_spec_mat[main_set_idx, ]
rownames(raman_main_set)
raman_test_set <- raman_spec_mat[-main_set_idx, ]
rownames(raman_test_set)
```

@@

```{r sets-show-knn}
train_idx <- grep("_1|_2|_01|_04|_06|_10", rownames(raman_spec_mat))

@@

>>>>

main_dir <- "C:/Users/thiss/Documents/Paracetamol_subset" # Ricardo laptop
ms_dir <- paste0(main_dir, "/ms")
ms_files <- list.files(ms_dir, pattern = ".mzML$", full.names = TRUE)
raman_dir <- paste0(main_dir, "/raman")
raman_files <- list.files(raman_dir, pattern = ".asc$", full.names = TRUE)
```

@@

```{r sets-show}
main_set_idx <- c(c(1:9), 13, 15)

@@

```{r sets-show-knn}
train_idx <- grep("_1|_2|_01|_06|_07|_10", rownames(fused_mat))

@@

```{r sets-show}
main_set_idx <- c(c(1:9), 13, 15)
ms_main_set <- ms_spec_mat[main_set_idx, ]
rownames(ms_main_set)
ms_test_set <- ms_spec_mat[-main_set_idx, ]
rownames(ms_test_set)
```

@@

```{r sets-show-knn}
train_idx <- grep("_1|_2|_01|_06|_07|_10", rownames(ms_spec_mat))

@@

```{r sets-show}
main_set_idx <- c(c(1:9), 13, 15)
raman_main_set <- raman_spec_mat[main_set_idx, ]
rownames(raman_main_set)
raman_test_set <- raman_spec_mat[-main_set_idx, ]
rownames(raman_test_set)
```

@@

```{r sets-show-knn}
train_idx <- grep("_1|_2|_01|_06|_07|_10", rownames(raman_spec_mat))

@@

```{r}

```
